Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-02-21 doc/GMP2015/revision_1/s06_problempinning.tex
Finished and submitted revision 1.

\section{Application: Finding completions of underconstrained glassy structures to isostatic}
\label{sec:bodypin}
% \bibliography{paper}

\begin{figure}\centering
    \includegraphics[width=0.4\linewidth]{img/Silica}\hspace{0.5cm}
    \raisebox{0.3\height}{\includegraphics[width=0.2\linewidth]{img/Silicon_tetrahedron}}
    \caption{Example of a single monolayer of a Silica (silicon and oxygen) glassy structure. This can be thought of as a triangle-multipin qusec where the Silicon atoms are the triangles and the Oxygen atoms are the pins. Not shown here are other monolayers stacked on this one. Each Silicon atom has the structure seen to the right, and so binds to another Oxygen atom in an adjacent monolayer. Pictures taken from \cite{silica_figure} and \cite{tetra_silica_figure}.}
    \label{fig:silica_glass}
\end{figure}

@@

In all cases, we are specifically interested in how to add additional constraints resulting isostatic structure with a small DR-plan, so a realization can be found and stress and other property design can be efficient. To answer these questions, we first introduce the qusecs that are used to model these materials. We will discuss Item 2 in detail in this section.

\begin{figure}\centering
    (a)
    \begin{subfigure}{0.2\linewidth}
        \includegraphics[width=\linewidth]{img/pentl1}
    \end{subfigure}
    %
    $\rightarrow$
    \begin{subfigure}{0.2\linewidth}
        \includegraphics[width=\linewidth]{img/pentl2}
    \end{subfigure}
    %

    (b)
    \begin{subfigure}{0.8\linewidth}
        \includegraphics[width=\linewidth]{img/pentawesome}
    \end{subfigure}
    \caption{Examples of self-similarity via repeated subdivision. In (a), simple subdivision that does not guarantee isostaticity. In (b), a more complicated scheme is used, ensuring that the resulting graph is isostatic but not  tree-decomposable. Credit to \cite{subdivision_paper} for (a).}
    \label{fig:subdivision}
\end{figure}

@@

\begin{definition}
    A \dfn{body-hyperpin qusecs} is a constraint system where the objects are rigid bodies some subsets of which are pinned together by pins.
\end{definition}

\begin{remark}\label{rem:bodypin_is_barjoint}
    A body-hyperpin qusecs is a special case of bar-joint qusecs of the
    first 5 sections. As such, the DR-planning for isostatics discussed in Section
    \ref{sec:DRP} is unchanged and the results of Section \ref{sec:recomb} will still go through with slight modifications.
\end{remark}

@@

    Such a body-pin graph can also be seen as a \dfn{body-bar graph} where the bodies are the original bodies and each pin represents 2 bars from one body to another. Such body-bar graphs with 1 and 2-dof can be characterized by being $(3,4)$ and $(3,5)$-tight respectively \cite{Lee:2007:PGA} \cite{streinu2009sparse}, defined in Section  \ref{sec:prelim}.
\end{definition}

@@

\begin{definition}
    A \dfn{$(k,l)$-tight DR-plan} is one in which each child node is either a vertex maximal proper $(k,l)$-tight sub-graph of the parent node or it is trivial. In our case, the trivial nodes are just the bodies.
\end{definition}

We can develop the notion of a canonical DR-plan when the hypergraph is $(k,l)$-sparse (i.e., combinatorially independent) using certain notion of trivial and non-trivial intersections and $(k,l)$-tightness conditions similar to the way we did in Section \ref{sec:DRP}, provided such $(k,l)$-sparse graphs are matroidal -- conditions given in \cite{Lee:2007:PGA}. In particular, we can define canonical DR-plans with similar properties for the 1 and 2-dof body-pin and triangle-hyperpin systems defined above.

\begin{observation}
\label{obs:bodypin_drp}
    For the 1-dof body-pin graphs described above that are $(3,4)$-sparse, a $(3,4)$-tight canonical DR-plan exists where every node of a $(3,4)$-sparse graph satisfies one of the following: (1) its children are 2 proper vertex maximal 1-dof graphs that intersect on another 1-dof graph; or (2) its children are all of the proper maximal 1-dof sub-graphs, pairwise sharing at most one body.
\end{observation}

@@

The strong Church-Rosser property holds making all canonical DR-plans optimal:
%
\begin{remark}\label{rem:1dofcanon}
    When the input is independent, all $(3,4)$-tight canonical DR-plans are optimal. We can find such a DR-plan in the same time complexity as the $(2,3)$-tight case for bar-joint graphs discussed in Section \ref{sec:DRP}. This is because such $(3,4)$-tight graphs are matroidal and have a pebble game, shown in \cite{Lee:2007:PGA}.
\end{remark}

@@

\begin{figure*}\centering
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/bodypin}
        \caption{}\label{fig:bodypindrp:a}
    \end{subfigure}
    %
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/bodypin_graph}
        \caption{}\label{fig:bodypindrp:b}
    \end{subfigure}
    %
    \begin{subfigure}{0.35\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/bodypin_drp}
        \caption{}\label{fig:bodypindrp:c}
    \end{subfigure}
    %
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/bodypin2}
        \caption{}\label{fig:bodypindrp:d}
    \end{subfigure}
    %
    \caption{(\ref{fig:bodypindrp:a}) is a 1-dof body-pin graph. (\ref{fig:bodypindrp:b}) is the corresponding body-bar graph explained in Definition \ref{def:body-pin}. (\ref{fig:bodypindrp:c}) is the 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (\ref{fig:bodypindrp:d}) is the result of adding one such body to the bold-faced node.}
    %
\end{figure*}

The above discussion leads to the main theorem:
\begin{theorem}
\label{thm:1dofcase}
    Given a 1-dof body-pin or triangle-multipin graph $G$ and corresponding 1-dof DR-plan $T$, there is a quadratic algorithm for the 1-dof optimal completion problem of Section \ref{sec:recomb}.
\end{theorem}

@@

\begin{observation}
\label{obs:2dof_case}
    For the 2-dof case, if a similar statement to Remark \ref{rem:1dofcanon} can be made, then Theorem \ref{thm:1dofcase} is true for 2-dof as well.
\end{observation}

@@

\begin{observation}
\label{obs:algebraic_completion}
    While the proof for Theorem \ref{thm:1dofcase} gives us a DR-plan for the isostatic completion with minimum fan-in, (a reasonable measure of algebraic complexity), a more nuanced measure that treats solutions of 1-dof and 2-dof systems as 1- or 2- parameter families would no longer permit the algorithm given in the proof. In particular the complexity of the standard algorithm in the $k$-dof case would be exponential in $k$ (even if that case were matroidal and an optimal DR-plan is known).
\end{observation}

>>>>

\section{Application: Finding completions of underconstrained glassy structures from underconstrained to isostatic}
\label{sec:bodypin}

\notetoreviewer{Changed section title from ``Application: Finding completions of underconstrained glassy structures to isostatic''}
% \bibliography{paper}

\ClearMyMinHeight
\SetMyMinHeight{.3}{img/silica}
\SetMyMinHeight{.2}{img/Silicon_tetrahedron}

\begin{figure}\centering
    \includegraphics[height=\myMinHeight]{img/Silica}
    \hspace{0.5cm}
    \includegraphics[height=\myMinHeight]{img/Silicon_tetrahedron}
    % \raisebox{0.25\height}{
    %     \includegraphics[height=\myMinHeight]{img/Silicon_tetrahedron}
    % }
    \caption{Example of a single monolayer of a silica (silicon and oxygen) glassy structure. This can be thought of as a triangle-multipin qusecs where the silicon atoms are the triangles and the oxygen atoms are the pins. Not shown here are other monolayers stacked on this one. Each silicon atom has the structure seen to the right, and so binds to another oxygen atom in an adjacent monolayer. Pictures taken from \cite{silica_figure} and \cite{tetra_silica_figure}.}
    \label{fig:silica_glass}
\end{figure}

@@

In all cases, we are specifically interested in how to add additional constraints \addin{such that} the resulting isostatic structure \cutout{with} \addin{has} a small DR-plan\cutout{, so} \addin{; this way} a realization can be found\addin{, allowing efficient} \cutout{and} stress and other property design\cutout{ can be efficient}. To answer these questions, we first introduce the qusecs that are used to model these materials. We will discuss \cutout{Item 2} \addin{item (2)} in detail in this section.

% \begin{figure}\centering
%     (a)
%     \begin{subfigure}{0.2\linewidth}
%         \includegraphics[width=\linewidth]{img/pentl1}
%     \end{subfigure}
%     %
%     $\rightarrow$
%     \begin{subfigure}{0.2\linewidth}
%         \includegraphics[width=\linewidth]{img/pentl2}
%     \end{subfigure}
%     %

%     (b)
%     \begin{subfigure}{0.8\linewidth}
%         \includegraphics[width=\linewidth]{img/pentawesome}
%     \end{subfigure}
%     \caption{Examples of self-similarity via repeated subdivision. In (a), simple subdivision that does not guarantee isostaticity. In (b), a more complicated scheme is used, ensuring that the resulting graph is isostatic but not  tree-decomposable. Credit to \cite{subdivision_paper} for (a).}
%     \label{fig:subdivision}
% \end{figure}

\begin{figure}\centering
    \begin{subfigure}{0.35\linewidth}
        $
        \vcenter{\hbox{\includegraphics[width=.4\linewidth]{img/pentl1}}}
        % \raisebox{-.5\height}{\scalebox{1}{$\rightarrow$}}
        \vcenter{\hbox{$\rightarrow$}}
        \vcenter{\hbox{\includegraphics[width=.4\linewidth]{img/pentl2}}}
        $
        \caption{}\label{fig:subdivision:simple}
    \end{subfigure}
    \begin{subfigure}{0.55\linewidth}
        \includegraphics[width=\linewidth]{img/pentawesome}
        \caption{}\label{fig:subdivision:complicated}
    \end{subfigure}
    \caption{Examples of self-similarity via repeated subdivision. In (\ref{fig:subdivision:simple}) \cite{subdivision_paper}, there is a simple subdivision scheme that does not guarantee isostaticity. In (\ref{fig:subdivision:complicated}), a more complicated scheme is used, ensuring that the resulting graph is isostatic but not  tree-decomposable.}
    \label{fig:subdivision}
\end{figure}

@@

\begin{definition}
    A \dfn{body-hyperpin qusecs} is a constraint system where the objects are rigid bodies, some subsets of which are pinned together by pins.
\end{definition}

\begin{remark*}\label{rem:bodypin_is_barjoint}
    A body-hyperpin qusecs is a special case of bar-joint qusecs of the first 5 sections. As such, the DR-planning for isostatics discussed in Section \ref{sec:DRP} is unchanged and the results of Section \ref{sec:recomb} will still go through with slight modifications.
\end{remark*}

@@

    Such a body-pin graph\addin{, $G_{BP}$,} can also be seen as a \dfn{body-bar graph}\addin{, $G_{BB}$,} where the bodies \addin{of $G_{BB}$} are the original bodies \addin{of $G_{BP}$} and each pin \cutout{represents 2 bars from one body to another} \addin{between bodies in $G_{BP}$ are replaced with 2 bars in $G_{BB}$ between the same bodies}.
    Such body-bar graphs with 1 and 2-dof can be characterized by being $(3,4)$ and $(3,5)$-tight respectively \cite{Lee:2007:PGA} \cite{streinu2009sparse} (defined in \ref{sec:appendix:defs}). \addin{See Figure \ref{fig:bodypindrp:b}.}
\end{definition}

@@

\begin{definition}
    A \dfn{$(k,l)$-tight DR-plan} is one in which each child node is either a vertex maximal proper $(k,l)$-tight sub-graph of the parent node or it is trivial. In our case, the trivial nodes are \cutout{just} the bodies.
\end{definition}

We can develop the notion of a canonical DR-plan when the hypergraph is $(k,l)$-sparse (i.e., combinatorially independent) using certain notion of trivial and non-trivial intersections and $(k,l)$-tightness conditions similar to the way we did in Section \ref{sec:DRP}, provided such $(k,l)$-sparse graphs are matroidal (conditions given in \cite{Lee:2007:PGA}). In particular, we can define canonical DR-plans with similar properties for the 1 and 2-dof body-pin and triangle-hyperpin systems defined above.

\begin{observation*}
\label{obs:bodypin_drp}
    For the 1-dof body-pin graphs described above that are $(3,4)$-sparse, a $(3,4)$-tight canonical DR-plan exists where every node of a $(3,4)$-sparse graph satisfies one of the following: (1) its children are 2 proper vertex maximal 1-dof graphs that intersect on another 1-dof graph; or (2) its children are all of the proper maximal 1-dof sub-graphs, pairwise sharing at most one body.
\end{observation*}

@@

The strong Church-Rosser property holds\addin{,} making all canonical DR-plans optimal:
%
\begin{remark}\label{rem:1dofcanon}
    When the input is independent, all $(3,4)$-tight canonical DR-plans are optimal. We can find such a DR-plan in the same time complexity as the $(2,3)$-tight case for bar-joint graphs discussed in Section \ref{sec:DRP}. This is because such $(3,4)$-tight graphs are matroidal and have a pebble game\cutout{, shown in} \cite{Lee:2007:PGA}.
\end{remark}

@@

\begin{figure*}\centering
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/bodypin}
        \caption{}\label{fig:bodypindrp:a}
    \end{subfigure}
    %
    \hfill
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/bodypin_graph}
        \caption{}\label{fig:bodypindrp:b}
    \end{subfigure}
    %
    \hfill
    \begin{subfigure}{0.35\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/epsfromtikz/bodypin_drp}
        \caption{}\label{fig:bodypindrp:c}
    \end{subfigure}
    %
    \hfill
    \begin{subfigure}{0.2\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/bodypin2}
        \caption{}\label{fig:bodypindrp:d}
    \end{subfigure}
    %
    \caption{(\ref{fig:bodypindrp:a}) A 1-dof body-pin graph. (\ref{fig:bodypindrp:b}) The corresponding body-bar graph, explained in Definition \ref{def:body-pin}. (\ref{fig:bodypindrp:c}) The 1-dof DR-plan for the graph. In this case, to obtain an isostatic system, we would need to add a body and 2 pins to one of the nodes in the second level. (\ref{fig:bodypindrp:d}) The result of adding one such body to the bold-faced node.}
    \label{fig:bodypindrp}
    %
\end{figure*}

The above discussion leads to the main theorem:
\begin{theorem*}
\label{thm:1dofcase}
    Given a 1-dof body-pin or triangle-multipin graph \cutout{$G$} and corresponding 1-dof DR-plan \cutout{$T$}, there is a quadratic algorithm for the 1-dof optimal completion problem of Section \ref{sec:recomb}.
\end{theorem*}

@@

\begin{observation*}
\label{obs:2dof_case}
    For the 2-dof case, if a similar statement to Remark \ref{rem:1dofcanon} can be made, then Theorem \ref{thm:1dofcase} is true for 2-dof as well.
\end{observation*}

@@

\begin{observation*}
\label{obs:algebraic_completion}
    While the proof for Theorem \ref{thm:1dofcase} gives us a DR-plan for the isostatic completion with minimum fan-in, (a reasonable measure of algebraic complexity), a more nuanced measure that treats solutions of 1-dof and 2-dof systems as 1 or 2 parameter families would no longer permit the algorithm given in the proof. In particular the complexity of the standard algorithm in the $k$-dof case would be exponential in $k$ (even if that case were matroidal and an optimal DR-plan is known).
\end{observation*}

### 2015-02-21 doc/GMP2015/revision_1/s07_pinnedline.tex
Finished and submitted revision 1.

\section{Application: finding optimal DR-plans and realizations for cross-linking microfibrils }
\label{sec:pinnedline}

The canonical DR-plan of Section \ref{sec:DRP} can also be applied to analyze and solve the structure of  cross-linking collagen and cellulose microfibrils in animal and plant cell walls, and actin filaments in the cytoskeleton by modeling these structures as \dfn{pinned line-incidence systems}.

@@

\ClearMyMinHeight
\SetMyMinHeight{.45}{img/AFM_Innventia_nanocellulose}
\SetMyMinHeight{.45}{img/crosslink}

\begin{figure}\centering%
    %
    \begin{subfigure}{0.45\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/AFM_Innventia_nanocellulose}
        \caption{}\label{fig:cellulose}
    \end{subfigure}%
    %
    \hfill
    \begin{subfigure}{0.45\linewidth}\centering
        \includegraphics[height=\myMinHeight]{img/crosslink}
        \caption{}\label{fig:crosslink}
    \end{subfigure}%
    %
    \caption{(\ref{fig:cellulose}) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \cite{wikimediacommons2010afm}. (\ref{fig:crosslink}) Cross-linking of cellulose microfibrils \cite{wikimediacommons2007plant}.}
\end{figure}%

@@

\begin{figure}\centering
    \includegraphics[width=.7\linewidth]{img/pinned}
    \caption{An isostatic pinned line-incidence graph.}
    \label{fig:pinned_line}
\end{figure}

@@

Theorem~\ref{theorem:main} holds for  pinned line-incidence graphs with the above modified definition. The proof is similar to the original proof (in \ref{theorem:main:proof}) using the same set of lemmas and
%
%\begin{corollary}\label{cor:pinned}
%Given a isostatic pinned line-incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
%\begin{enumerate}
%    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$.
%    \item if $C_i \cap C_j$ is isostatic then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
%\end{enumerate}
%\end{corollary}
%
the following modified version of Observation~\ref{lemma:union_intersection},
% observation, which
%serves a similar function to Observation~\ref{lemma:union_intersection} in Section~\ref{sec:DRP}
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection},
which  can be proved using a simple counting based argument.

\begin{observation}\label{lem:pinned_union_intersection}
    Let $F_i$ and $F_j$ to be subgraphs of the same isostatic graph $F$, where each of them can be either a single edge or a connected isostatic subgraph. There are only two possible cases:
    (1) At least one of $F_i$, $F_j$ is an edge, if and only if $F_i \cup F_j$ is underconstrained, if and only if $F_i \cap F_j$ is trivial; and (2) both $F_i$ and $F_j$ are isostatic, if and only if $F_i \cup F_j$ is isostatic, if and only if $F_i \cap F_j$ is isostatic.
    %The following table summarizes all bijections:
    %\setlength{\tabcolsep}{3pt}
    %{\small
    %\begin{center}
    %\begin{tabular}{|p{2.8cm}|c|p{2.3cm}|}
    %\hline
    %\textbf{Property of $F_i,F_j$} & \textbf{$F_i\cup F_j$} & \centering \textbf{$F_i\cap F_j$}  \tabularnewline \hline
    % \centering--- &  \sout{overconstrained}          &  \centering --- \tabularnewline \hline
    %at least one of $F_i,F_j$ is an edge & underconstrained       &  \centering a vertex (underconstrained)  \tabularnewline \hline
    %both $F_i$ and $F_j$ are wellconstrained & wellconstrained        &  \centering wellconstrained  \tabularnewline \hline
    % \centering --- & ---                     &  \centering \sout{underconstrained} \tabularnewline \hline
    %\end{tabular}
    %\end{center}
    %}
    %\setlength{\tabcolsep}{6pt}
\end{observation}

Given Lemma~\ref{lem:pinned_union_intersection}, % and the modified definition of DR-plan,
Lemma~\ref{lemma:wc_intersection_is_C} and \ref{lemma:uc_intersection_makes_all_uc} straightforwardly extend to  pinned line-incidence graphs. The proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for pinned line-incidence graphs is given in~\ref{sec:appendix_pinned}.
%The following lemma serves as Lemma~ for pinned line-incidence and can be proved similarly.
%\begin{lemma}
%\label{lem:vertex_intersection}
%If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
%\end{lemma}
%Given Lemma~\ref{lemma:wc_intersection_makes_all_wc} and Lemma~\ref{lemma:uc_intersection_makes_all_uc},
Thus it is straightforward to adapt the proof of Theorem~\ref{theorem:main} to  pinned line-incidence graphs.
%thus proving Corollary~\ref{cor:pinned}.
%
Consequently, we can efficiently find the optimal DR-plan for  pinned line-incidence graphs using basically the same algorithm as for  bar-joint graphs.

>>>>

\section{Application: Finding optimal DR-plans and realizations for cross-linking microfibrils }
\label{sec:pinnedline}

The canonical DR-plan of Section \ref{sec:DRP} can also be applied to analyze and solve the structure of
\cutout{cross-linking collagen and cellulose microfibrils in animal and plant cell walls, and actin filaments in the cytoskeleton}
\addin{cross-linking collagen microfibrils in animals, cellulose microfibrils in plant cell walls, and actin filaments in the cytoskeleton}
by modeling these structures as \dfn{pinned line-incidence systems}.

@@

\ClearMyMinHeight
\SetMyMinHeight{.32}{img/AFM_Innventia_nanocellulose}
\SetMyMinHeight{.32}{img/crosslink}
\SetMyMinHeight{.32}{img/pinned}

\begin{figure}\centering%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/AFM_Innventia_nanocellulose}
    \caption{}\label{fig:cellulose}
\end{subfigure}\hfill%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/crosslink}
    \caption{}\label{fig:crosslink}
\end{subfigure}\hfill%
\begin{subfigure}{0.32\linewidth}\centering
    \includegraphics[height=\myMinHeight]{img/pinned}
    \caption{}
    \label{fig:pinned_line}
\end{subfigure}%
\caption{\notetoreviewer{Combined 2 figures.} (\ref{fig:cellulose}) Microfibrils of carboxymethylated nanocellulose adsorbed on a silica surface \cite{wikimediacommons2010afm}. \ref{fig:crosslink} Cross-linking of cellulose microfibrils \cite{wikimediacommons2007plant}. \ref{fig:pinned_line} An isostatic pinned line-incidence graph\addin{, representing fibrils and their attachments.}}
\end{figure}%

@@

% \begin{figure}\centering
%     \includegraphics[width=.7\linewidth]{img/pinned}
%     \caption{An isostatic pinned line-incidence graph.}
%     \label{fig:pinned_line}
% \end{figure}

@@

Theorem~\ref{theorem:main} holds for pinned line-incidence graphs with \cutout{the above} \addin{this} modified definition. The proof is similar to the original proof (in Section~\ref{sec:DRP}) using the same set of lemmas and
%
%\begin{corollary}\label{cor:pinned}
%Given a isostatic pinned line-incidence graph, for node $C$ in $OptimalDRP(G)$ and the children of $C$ in $CompleteDRP(C)$ labeled as $C_1,\ldots,C_N$
%\begin{enumerate}
%    \item if $C_i \cap C_j$ is trivial then all $C_1,\ldots,C_N$ are children of $C$ in $OptimalDRP(G)$.
%    \item if $C_i \cap C_j$ is isostatic then any two out of $C_1,\ldots,C_N$ will be the only children of $C$ in $OptimalDRP(G)$.
%\end{enumerate}
%\end{corollary}
%
the following modified version of Observation~\ref{lemma:union_intersection},
% observation, which
%serves a similar function to Observation~\ref{lemma:union_intersection} in Section~\ref{sec:DRP}
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection},
which  can be proved using a simple counting based argument.

\begin{observation}\label{lem:pinned_union_intersection}
    Let $F_i$ and $F_j$ to be subgraphs of the same isostatic graph $F$, where each of them can be either a single edge or a connected isostatic subgraph. There are only two possible cases:
    (1) at least one of $F_i$, $F_j$ is an edge, if and only if $F_i \cup F_j$ is underconstrained, if and only if $F_i \cap F_j$ is trivial; and (2) both $F_i$ and $F_j$ are isostatic, if and only if $F_i \cup F_j$ is isostatic, if and only if $F_i \cap F_j$ is isostatic.
    %The following table summarizes all bijections:
    %\setlength{\tabcolsep}{3pt}
    %{\small
    %\begin{center}
    %\begin{tabular}{|p{2.8cm}|c|p{2.3cm}|}
    %\hline
    %\textbf{Property of $F_i,F_j$} & \textbf{$F_i\cup F_j$} & \centering \textbf{$F_i\cap F_j$}  \tabularnewline \hline
    % \centering--- &  \sout{overconstrained}          &  \centering --- \tabularnewline \hline
    %at least one of $F_i,F_j$ is an edge & underconstrained       &  \centering a vertex (underconstrained)  \tabularnewline \hline
    %both $F_i$ and $F_j$ are wellconstrained & wellconstrained        &  \centering wellconstrained  \tabularnewline \hline
    % \centering --- & ---                     &  \centering \sout{underconstrained} \tabularnewline \hline
    %\end{tabular}
    %\end{center}
    %}
    %\setlength{\tabcolsep}{6pt}
\end{observation}

Given \cutout{Lemma} \addin{Observation}~\ref{lem:pinned_union_intersection}, % and the modified definition of DR-plan,
Lemma \addin{\ref{lemma:combined_lemma}, Point} \ref{lemma:wc_intersection_is_C} and \ref{lemma:uc_intersection_makes_all_uc}\addin{,} straightforwardly extend to pinned line-incidence graphs. The proof of Point~\ref{lemma:wc_intersection_makes_all_wc} for pinned line-incidence graphs is given in~\ref{sec:appendix_pinned}.
%The following lemma serves as Lemma~ for pinned line-incidence and can be proved similarly.
%\begin{lemma}
%\label{lem:vertex_intersection}
%If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
%\end{lemma}
%Given Lemma~\ref{lemma:wc_intersection_makes_all_wc} and Lemma~\ref{lemma:uc_intersection_makes_all_uc},
Thus it is straightforward to adapt the proof of Theorem~\ref{theorem:main} to  pinned line-incidence graphs.
%thus proving Corollary~\ref{cor:pinned}.
%
Consequently, we can efficiently find the optimal DR-plan for  pinned line-incidence graphs using basically the same algorithm as for  bar-joint graphs.

### 2015-02-21 doc/GMP2015/revision_1/s08_conclusion.tex
Compiles with Elsevier format. Got rid of minor spacing errors. Converted tikz figures to eps. Aligned subfigures. Etc. It's looking good! Now to consider major changes.
Finished and submitted revision 1.

\section{Conclusion}
% \bibliography{paper}

We have clarified the main source of complexity for the optimal DR-plan and recombination problems. For the former problem, when there are no overconstraints, (as is the case for 2D qusecs whose realizations are many common types of layered materials), we defined a canonical DR-plan and showed that such canonical DR-plans are guaranteed to be optimal, a strong Church-Rosser property giving an efficient (\candrpcomplexity) algorithm to find an optimal  DR-plan that satisfies other desirable characteristics.

We have also described a novel method of efficiently realizing a 2D qusecs from the optimal DR-plan by modifying the otherwise nondecomposable system that recombines the solved child systems at a node of a DR-plan These results rely on a recent theory of Convex Cayley Configuration spaces. Relationships and reductions between these and previously studied problems were formally clarified.

@@

In Appendix B (provided in the attachment) we present open problems for future work.

>>>>

\section{Conclusion}
\label{sec:conclusion}

We have clarified the main source of complexity for the optimal DR-plan and recombination problems. For the former problem, when there are no overconstraints\cutout{,} (as is the case for 2D qusecs whose realizations are many common types of layered materials), we defined a canonical DR-plan and showed that \cutout{such} \addin{any} canonical DR-plan\cutout{s are} \addin{is} guaranteed to be optimal, \addin{which is} a strong Church-Rosser property\addin{. This gives} \cutout{giving} an efficient (\candrpcomplexity) algorithm to find an optimal DR-plan that satisfies other desirable characteristics.

We have also described a novel method of efficiently realizing a 2D qusecs from the optimal DR-plan by modifying the otherwise nondecomposable system that recombines the solved child systems at a node of a DR-plan. These results rely on a recent theory of Convex Cayley Configuration spaces. Relationships and reductions between these and previously studied problems were formally clarified.

@@

% \section{Open Problems}
\subsection{Open Problems}
\label{sec:appendix:b}
\label{sec:futurework}

\notetoreviewer{The following section was moved in from the appendix.}

One open problem comes from Section \ref{sec:DRP}:
\begin{openproblem}
    Is there a lower complexity algorithm than \candrpcomplexityv\ to find the canonical DR-plan of isostatic 2D bar-joint graphs?
\end{openproblem}

A few natural  open questions concern the following common theme that runs through the paper:

\begin{openproblem}
    For fixed $k$ we have polynomial time optimal DR-planning \addin{(Section~\ref{sec:DRP})}, recombination (modification) in the presence of $k$ overconstraints\cutout{ (Section X}, optimal modification for decomposition {\sl OMD}$_k(G)$, when at most $k$ constraints are removed \addin{(Section~\ref{sec:recomb})} and also optimal completion using at most $k\le 2$ constraints in the body-pin and triangle-multipin cases under a modified measure for optimizing the DR-plan \addin{(Section~\ref{sec:table})}. However, \addin{in the running time of all of these algorithms,} $k$ appears in the exponent\cutout{ for the straightforward algorithms for these problems}.
\end{openproblem}

One problem in the above theme is from Section \ref{sec:bodypin}.
\begin{openproblem}
    What is the complexity of the optimal completion problem when the given graph has more than 2-dofs? Our proof for the 1 and 2-dof cases relied heavily on the matroidal properties of their corresponding $(k,l)$-tightness. For higher number of dofs, the $(k,l)$ characterization is no longer matroidal \cite{Lee:2007:PGA}. As a result, the major obstacle is that there is no easy way of obtaining an optimal or canonical $k$-dof DR-plan in general. Even assuming such  a DR-plan is available, if higher dofs had the same characteristics, Observation \ref{obs:algebraic_completion} raises questions about the correct measure of DR-plan size that captures algebraic complexity for recombining graphs with many dofs (this is not an issue in the isostatic case). Unless some restrictions can be found and taken advantage of, the $k$-dof optimal completion problem would  have complexity exponential in $k$.
\end{openproblem}

Another problem from the above theme is from Section \ref{sec:recomb}
\begin{openproblem}
    What is the complexity of the restricted OMD (optimal modification for decomposition) problem? This has the potential to be difficult. For example, when the isostatic completion is required to be a 2-tree the restricted OMD problem is reducible to the maximum spanning series-parallel subgraph problem shown by \cite{cai1993spanning} to be NP-complete even if the input graph is planar of maximum degree at most 6. However, since the OMD problem has other input restrictions such as not having any proper isostatic subgraphs, it is not clear if the reverse reduction exists and hence it is unclear whether the OMD problem is NP-complete.

    The same holds for the restricted OMD problem where the isostatic completion is required to be a tree-decomposable graph of low Cayley complexity (i.e, have special, small DR-plans). One potential obstacle to an indecomposable graph $G$'s membership in the restricted OMD$_k$ for small $k$ is if $G$ is tri-connected and has large girth. In fact, 6-connected (hence rigid) graphs with arbitrarily large girth have been constructed in \cite{servatius2000rigidity}.
\end{openproblem}

The next is the reverse direction of Observation \ref{obs:OC_to_OMD} in Section \ref{sec:table}.
\begin{openproblem}
    Is the OMD (optimal modification for decomposition) problem reducible to the OC (Optimal completion) problem?
\end{openproblem}

More general problem directions are the following.
\begin{openproblem}
    Combinatorial rigidity for periodic structures is an active area of research. This paper motivates a study of the rigidity of self-similar structures, with self-similar groups replacing periodic groups.
\end{openproblem}

\begin{openproblem}
    The pinned line incidence structures of Section \ref{sec:pinnedline}, for example in the case of collagen microfibrils, whose function is elastic contraction, should be considered congruent under projective transformations. I.e, the projective group should be factored out as a trivial motion in a new project for extending the combinatorial rigidity characterization of such systems. (Currently we permit no trivial motions at all).
\end{openproblem}

\begin{openproblem}
    Experimental validation (either computationally or physical experiments) of predications based on the material model and theory used in this paper. This can be done by modeling known materials and putting stresses on them, seeing if the prediction is observed in the real material. Or, our theory could be used to design new materials, which can be tested to see if they possess predicted properties.
\end{openproblem}
